Quantum Pseudo-Telepathy

### 2023-06-30 paper/main.tex
Paper => fix circuits

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}[column sep=0.25cm]
      \lstick{\(A_{0}\)}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{Y}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{S}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S^*}
      \\
      \lstick{\(A_{1}\)}
      & \gate{Y}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{0}}
      & \targ{}
      & \gate{Y}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{1}}
      & \targ{}
      & \gate{S}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{2}}
      & \targ{}
      & \gate{H}
      & \gate{S^*}
    \end{quantikz}
    \caption{Quantum circuit for measuring the third row.\label{fig:circ-row2}}
  \end{figure}

>>>>

  \begin{figure}[htbp]
    \centering
    \begin{quantikz}[column sep=0.25cm]
      \lstick{\(A_{0}\)}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{Y}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{Y}
      & \gate{S}
      & \gate{H}
      & \ctrl{1}
      &
      & \ctrl{1}
      & \gate{H}
      & \gate{S^*}
      \\
      \lstick{\(A_{1}\)}
      & \gate{Y}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{0}}
      & \targ{}
      & \gate{Y}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{1}}
      & \targ{}
      & \gate{H}
      & \gate{S}
      & \gate{H}
      & \targ{}
      & \metercw[label style={inner sep=1pt}]{a_{2}}
      & \targ{}
      & \gate{H}
      & \gate{S^*}
    \end{quantikz}
    \caption{Quantum circuit for measuring the third row.\label{fig:circ-row2}}
  \end{figure}
